title_uniform

### 2021-02-04 inst/examples/title_uniform.Rmd
change added

---
title: "title_uniform"
author: ""
date: "`r Sys.Date()`"
output: md_document
---

>>>>

---
title: "title_uniform"
output: md_document
---
* [Unique accepted titles](output.tables/title_accepted.csv): `r length(unique(df$title_uniform))`
 * [Unique discarded titles in original data](output.tables/title_discarded.csv) (excluding NA cases): `r as.vector(countLines(paste0(output.folder, "/title_discarded.csv")) - 1)` 
 * Original documents with non-NA titles: `r sum(!is.na(df$title_uniform))` / `r nrow(df)` (`r round(100*mean(!is.na(df$title_uniform)), 1)`%)
 * Original documents with missing (NA) titles `r sum(is.na(df$title_uniform))` / `r nrow(df)` documents (`r round(100*mean(is.na(df$title_uniform)), 1)`%)

Top-`r ntop` titles and their title counts.

```{r summarytitle, echo=FALSE, message=FALSE, warning=FALSE, fig.width=8, fig.height=6}
library(ggplot2)
theme_set(theme_bw(base_size = 12))
p <- top_plot(df, "title_uniform", ntop = ntop, log10 = TRUE)+
  labs(y = "Entries (n)", title = "Top titles")
print(p)
```
